Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-10-17 docs/paper/paper.tex
fix: typo

The first set of experiments performed on the GAN phase is the number of the augmented samples. In these experiments, we have augmented the proposed ANN system with a varying number of samples. According to these experiments we have reached the minimum MSE at 1000 samples. Adding further samples slightly reduces the performance while increasing the training time. The results of this experiment is demonstrated in Figure \ref{chart:gansamples} \hl{showing that the increasing number of augmented samples increases the performance to a point where it will start hurting the performance (>3000 samples). The reason behind this augmented samples are not perfect. They deviate from the actual data. However, up to a point, the performance impact of having low number of training samples out-weighs the imperfect data generated by GAN.} The number of augmented samples depends on the training samples that are available and can vary depending on the dataset used.

>>>>

The first set of experiments performed on the GAN phase is the number of the augmented samples. In these experiments, we have augmented the proposed ANN system with a varying number of samples. According to these experiments we have reached the minimum MSE at 1000 samples. Adding further samples slightly reduces the performance while increasing the training time. The results of this experiment is demonstrated in Figure \ref{chart:gansamples} \hl{showing that the increasing number of augmented samples increases the performance to a point where it will start hurting the performance ($>$ 3000 samples). The reason behind this augmented samples are not perfect. They deviate from the actual data. However, up to a point, the performance impact of having low number of training samples out-weighs the imperfect data generated by GAN.} The number of augmented samples depends on the training samples that are available and can vary depending on the dataset used.
